Fourmile Calibrations and Output

### 2025-04-25 fourmile_output_dec2024.Rmd
added pts based on performance to the flow type boxplots

# look at 2015, high snow year 
example <- gw %>%
  filter(year == 2016) %>%
  ungroup() %>% 
  dplyr::select(date, source,
         RD1cumsum,
         RD2cumsum,
         RG1cumsum,
         RG2cumsum) %>%
  pivot_longer(!c(date,source), names_to='flow_type',
               values_to='flow_cms') %>%
  mutate(source = if_else(source == 'grid_all',
                          'Gridded',
                          'Station'))

@@

example_yr <- ggplot(example,
       aes(x=date, y = flow_cms, color=source)) +
  geom_line() +
  facet_wrap(~flow_type, 
             scales = 'free_y',
             labeller = labeller(flow_type = facet_labels)) +
   geom_line(size=1, alpha=0.7) +  
  scale_color_manual(values = c("#0047AB", "orange")) +
    scale_x_date(date_labels = "%b %Y", 
               date_breaks = "2 month") +
  labs(x=element_blank(),
       y='Flow (cms)') +
  theme_bw(base_size = 16) +
  theme(
    legend.position = c(0.94, 0.1),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
  )

@@

gw_maxcumsum_letters <- gw_maxcumsum %>%
  group_by(source, flow_type) %>%
  mutate(max = max(flow_cms)) %>%
  distinct(flow_type, source, .keep_all = TRUE) %>%
    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
                           source == 'Gridded'),
                         3.5, max)) %>%
    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
                           source == 'Station'),
                         1.3, max)) %>%
  mutate(y_text = max * 1.07)

flow_box <- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1),
               outliers=F) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
  geom_text(data = gw_maxcumsum_letters, 
            aes(label=letter,
                y=y_text),
            position = position_dodge(width = 0.97),
            size = 6, 
            vjust = 0) + 
  facet_wrap(~flow_type, 
             scales = 'free',
             labeller = labeller(flow_type = facet_labels)) +
  labs(y = 'mm of water') + 
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    legend.position = c(0.94, 0.36),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))

@@

# ggsave('./figures/water_partition_boxplots.png',
#        dpi=600)

@@

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/water_partition_combine.png',
       dpi=600,
       width=12,
       height=12)

>>>>

# look at 2016, best performing year 
example <- gw %>%
  filter(year == 2016) %>%
  ungroup() %>% 
  dplyr::select(date, source,
         RD1cumsum,
         RD2cumsum,
         RG1cumsum,
         RG2cumsum) %>%
  pivot_longer(!c(date,source), names_to='flow_type',
               values_to='flow_cms') %>%
  mutate(source = if_else(source == 'grid_all',
                          'Gridded',
                          'Station'))

@@

example_yr <- ggplot(example,
       aes(x=date, y = flow_cms, color=source)) +
  geom_line() +
  facet_wrap(~flow_type, 
             scales = 'free_y',
             labeller = labeller(flow_type = facet_labels)) +
   geom_line(size=1, alpha=0.7) +  
  scale_color_manual(values = c("#0047AB", "orange")) +
    scale_x_date(date_labels = "%b %Y", 
               date_breaks = "2 month") +
  labs(x=element_blank(),
       y='mm of water') +
  theme_bw(base_size = 16) +
  theme(
    legend.position = c(0.94, 0.1),
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
  )

@@

perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nse_pbias_grid_statn_all.csv') %>%
  mutate(year = as.factor(year))

gw_maxcumsum <- left_join(gw_maxcumsum,
                          perf,
                          by = c('source',
                                 'year'))

gw_maxcumsum <- gw_maxcumsum %>%
  mutate(flow_cms = if_else(flow_type == 'yr_cum_RD1' &
                                flow_cms > 48,
                              NA,
                              flow_cms))

gw_maxcumsum_letters <- gw_maxcumsum %>%
  group_by(source, flow_type) %>%
  mutate(max = max(flow_cms)) %>%
  distinct(flow_type, source, .keep_all = TRUE) %>%
    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
                           source == 'Gridded'),
                         3.5, max)) %>%
    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
                           source == 'Station'),
                         1.3, max)) %>%
  mutate(y_text = max * 1.06)

flow_box <- ggplot(gw_maxcumsum, aes(x = source, y = flow_cms, fill = source)) +
  geom_boxplot(outliers=F,width=0.7) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
  geom_jitter(
    aes(shape = both),
    position = position_jitter(width = 0.25),
    size = 2.5,
    alpha = 0.7,
    stroke = 1,
    color = "black") +
  scale_shape_manual(values = c(
  "NSE + % bias unsatisfactory" = 4,
  "NSE + % bias satisfactory" = 16,
  "NSE satisfactory" = 1)) +
  geom_text(data = gw_maxcumsum_letters, 
            aes(label=letter,
                y=y_text),
            position = position_dodge(width = 0.97),
            size = 6, 
            vjust = 0) + 
  facet_wrap(~flow_type, 
             scales = 'free',
             labeller = labeller(flow_type = facet_labels)) +
  labs(y = 'mm of water') + 
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange"), guide = 'none') +
  theme(
    #legend.position = c(0.94, 0.36),
    legend.position = 'bottom',
    legend.text = element_text(size = 12),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.x = element_blank(),
    legend.spacing = unit(0.1, "lines"),
    legend.margin = margin(t = -8, r = 0, b = -2, l = 0)) +
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank()) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))

@@

# ggsave('./figures/water_partition_boxplsource()# ggsave('./figures/water_partition_boxplots.png',
#        dpi=600)

@@

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/water_partition_combine_pts.png',
       dpi=600,
       width=12,
       height=12)
